\textbf{Discovery of a disrupting open cluster far into the Milky Way halo:\\ a recent star formation event in the leading arm of the Magellanic stream?}

### 2018-11-09 ms.tex
data tables

% TODO
% - Sand, Seth, et al. Virgo: blue stars with nothing else
% - Split cluster into 2? Price-Whelan 1a and 1b?
% - discuss Blanco 1: high latitude, similar age, high binary fraction
% - Make a PGM for this model?
% - release data for the candidate members!

@@

We use an ensemble Markov chain Monte Carlo (MCMC) sampler \citep[\texttt{emcee};][]{emcee, Goodman:2010} to generate posterior samples over the parameters $(f, \bs{x}, s)$ using the likelihood defined above (\equationname~\ref{eq:likelihood}), and assuming the following prior probability distributions: uniform over the domain $(-5, 5)~\masyr$ for each component of $\bs{x}$, uniform in $f$, and uniform in log-$s$ over the domain $-6 < \ln s < 4$ (with $s$ in units of \masyr).
We run the sampler with 32 walkers for 256 steps as burn-in, then reset the sampler and run for an additional 512 steps.
We then thin the resulting chains by taking every 16th sample, leaving a total of 1024 samples; We use these samples to estimate the median posterior parameter values and uncertainties,
For the young cluster, we find $\bs{x} = (-0.56,  0.47) \pm (0.04, 0.02)~\masyr$, $\ln s = -3.8 \pm 0.9$, and $f = 0.14 \pm 0.02$.
The proper-motion dispersion is consistent with zero, and is likely unmeasured; 95\% of the posterior samples have $s < 0.09~\masyr$.

@@

@@

>>>>

% TODO: after submission
% - Split cluster into 2? Price-Whelan 1a and 1b?
% - discuss Blanco 1: high latitude, similar age, high binary fraction
% - Make a PGM for this model?

@@

We use an ensemble Markov chain Monte Carlo (MCMC) sampler \citep[\texttt{emcee};][]{emcee, Goodman:2010} to generate posterior samples over the parameters $(f, \bs{x}, s)$ using the likelihood defined above (\equationname~\ref{eq:likelihood}), and assuming the following prior probability distributions: uniform over the domain $(-5, 5)~\masyr$ for each component of $\bs{x}$, uniform in $f$, and uniform in log-$s$ over the domain $-6 < \ln s < 4$ (with $s$ in units of \masyr).
We run the sampler with 32 walkers for 256 steps as burn-in, then reset the sampler and run for an additional 512 steps.
We then thin the resulting chains by taking every 16th sample, leaving a total of 1024 samples; We use these samples to estimate the median posterior parameter values and uncertainties,
For the young cluster, we find $\bs{x} = (-0.56,  0.47) \pm (0.04, 0.02)~\masyr$, $\ln s = -3.8 \pm 0.9$, and $f = 0.14 \pm 0.02$.
The proper-motion dispersion is consistent with zero, and is likely unmeasured; 95\% of the posterior samples have $s < 0.09~\masyr$.
\tablename~\ref{tbl:gaiadata} contains a subset of the \gaia\ \DR{2} data for stars in the cluster field, with kinematic membership probabilities determined from this modeling procedure.

@@

\clearpage

@@

\begin{table}[h!]
    \centering
    \begin{tabular}{c | c | c | c | c | c | c | c | c}
        \multicolumn{9}{c}{\textbf{Catalog of \gaia\ sources and kinematic probability}}\\
        \texttt{source\_id} & \texttt{ra} & \texttt{dec} & \texttt{pmra} & \texttt{pmdec} & \texttt{G0} & \texttt{BP0} & \texttt{RP0} & \texttt{member\_prob} \\
        \tableline
        3462048793708019200 & 184.799 & -34.971 &  0.09 & -1.61 & 19.79 & 19.915 & 19.61 & 0.00 \\
        3462056696448285440 & 184.511 & -34.988 & -4.24 & -1.32 & 20.80 & 20.498 & 20.31 & 0.09 \\
        3462062670747949312 & 184.426 & -34.816 & -0.56 & -2.77 & 20.33 & 20.363 & 20.06 & 0.00 \\
        3462062709402484224 & 184.407 & -34.809 & -7.50 & -3.16 & 20.67 & 20.437 & 20.09 & 0.01 \\
        3462065904858152832 & 184.705 & -34.783 &  0.91 & -1.95 & 20.64 & 20.625 & 20.37 & 0.12 \\
        \multicolumn{9}{c}{...}\\
        \multicolumn{9}{c}{\textit{(5983 rows)}}
    \end{tabular}
    \caption{Select \gaia\ \DR{2} data and membership probabilities computed for all stars in the cluster region (see \figurename~\ref{fig:pm-members}).}
    \label{tbl:gaiadata}
\end{table}

\begin{table}[h!]
    \centering
    \begin{tabular}{c | c | c | c | c | c | c | c | c | c}
        \multicolumn{10}{c}{\textbf{Catalog of \decam\ photometry for point sources}}\\
        \texttt{name} & \texttt{ra} & \texttt{dec} & \texttt{g} & \texttt{g\_err} & \texttt{i} & \texttt{i\_err} & \texttt{control\_mask} & \texttt{cluster\_mask} & \texttt{member\_mask} \\
        \tableline
        J115311.06-283133.4 & 178.296 & -28.525 & 24.09 & 0.46 & 23.99 & 0.33 & True & False & False \\
        J115403.33-283553.8 & 178.513 & -28.598 & 25.27 & 0.29 & 22.70 & 0.04 & True & False & False \\
        J115424.21-283749.6 & 178.600 & -28.630 & 24.61 & 0.25 & 23.83 & 0.28 & True & False & False \\
        J115413.93-283343.6 & 178.558 & -28.562 & 25.37 & 0.41 & 22.76 & 0.05 & True & False & False \\
        J115419.62-283635.8 & 178.581 & -28.609 & 24.20 & 0.13 & 21.89 & 0.02 & True & False & False \\
        \multicolumn{10}{c}{...}\\
        \multicolumn{10}{c}{\textit{(51932 rows)}}
    \end{tabular}
    \caption{\decam\ photometry and sky positions for point sources in the observed \decam\ field.
    The boolean columns \texttt{control\_mask} and \texttt{cluster\_mask} are True when a given source is in the control or cluster CCDs, respectively (see \figurename~\ref{fig:decam-field}).
    The boolean column \texttt{member\_mask} is True when the source has a photometric membership probability $>0.5$ of belonging to the cluster stellar population (see \sectionname~\ref{sec:popmodel}).
    }
    \label{tbl:decamdata}
\end{table}
